Rapid technological progress in white light-emitting diodes \\ and its sources in innovation and technology spillovers

### 2023-01-29 2_SSL_EES/article/article_supplementary.tex
added innovations table to supplementary information

>>>>

\newpage
\section{Identified LED Innovations}

\begin{table}[H]
    \begin{tabularx}{\textwidth}{ |l|X|X|l|l| }
        \multicolumn{5}{c}{Forward Voltage Efficiency (VFE) $\eta_{Vf}$} \\
        \hline
            \textit{Year} & \textit{Breakthrough} & \textit{Affects} & \textit{S/O} & \textit{Source} \\
        \hline
            1983 & Indium Tin Oxide \newline Current Spreading Layer & Contact Resistance & Yes (T,S) & \cite{margalith1999indium}\\
        \hline
            1998 & Digited Electrodes & Contact Resistance & Weak & \cite{steigerwald2001electrode} \\
        \hline
            ongoing & Epitaxy Improvements \newline and better Doping & Polarization and \newline Bulk Resistance & No & I \\
        \hline
        $\sim$2000 & Silver p-Contacts & Contact Resistance & No & \cite{kondoh2001nitride} \\
        \hline
        \multicolumn{5}{c}{Light Extraction Efficiency (LEE) $\eta_{LE}$} \\
        \hline
            \textit{Year} & \textit{Breakthrough} & \textit{Affects} & \textit{S/O} & \textit{Source} \\
        \hline
            $<$ 2003 & Optimization for  \newline Cavity Effects & Other & No & I, \cite{Shen2003} \\
        \hline
            (1973) 1993 & "Chip \newline Randomization" & Total Reflection \newline Absorption & No & I, \cite{bergh1973surface}\cite{Schnitzer1993} \\
        \hline
            1993 & Thin-Film \newline Chip Architecture & Absorption & No & I, \cite{Schnitzer1993} \\
        \hline
            $<2001$ & Patterned Sapphire \newline Substrate  & Total Reflection \newline Absorption & Yes (T,S) & I, \cite{Tadatomo2001} \\
        \hline
            ongoing & Chip Design for \newline high LEE & Total Reflection \newline Absorption & No & I, \cite{Haerle2004} \\
        \hline
            $\sim$2000 & Silver p-Contacts & Absorption & No & I, \cite{kondoh2001nitride} \\
        \hline
        \multicolumn{5}{c}{Internal Quantum Efficiency (IQE) $\eta_{IQ}$} \\
        \hline
            \textit{Year} & \textit{Breakthrough} & \textit{Affects} & \textit{S/O} & \textit{Source} \\
        \hline
            1994 & DH & $>$ Radiative Recombination \newline Probability & No & \cite{Nakamura1994} \\
        \hline
            1996 & MQW & $>$ Radiative Recombination \newline Probability & No & \cite{Koike1996} \\
        \hline
            ongoing & Active Region \newline Doping & Both & No & I, \cite{schubert2018light} \\
        \hline
            ongoing & Epitaxy \newline Improvements & Both & No & I \\
        \hline
            ongoing & Chip Architecture \newline Improvements & Both & No & I \\
        \hline
        \multicolumn{5}{c}{(Phosphor) Conversion Efficiency (CE) $\eta_{C}$} \\
        \hline
            \textit{Year} & \textit{Breakthrough} & \textit{Affects} & \textit{S/O} & \textit{Source} \\
        \hline
            ongoing & Lower Current Density & Current Density & No & I \\
        \hline
            ongoing & Epitaxy \newline Improvements & $\ominus/\oplus$ Distribution \newline Defect Density & No & I, \cite{bhardwaj2016progress} \\
        \hline
            ongoing & Chip Architecture \newline Improvements  & $\ominus/\oplus$ Distribution \newline Defect Density & No & I, \cite{Wildeson2017} \\
        \hline
            $<$ 2017 & Defect Getting \newline Underlayer & Defect Density & No & I, \cite{haller2017burying} \\
        \hline
        \end{tabularx}
    \caption{Technology breakthroughs and spillovers related to improvements in forward voltage efficiency, light extraction efficiency, internal quantum efficiency and conversion efficiency. Year column indicates first identified use in solid-state lighting. S/O column indicates if the breakthrough has been identified as a spillover. Source column additionally indicates if the spillover has been identified as part of an expert interview (I). Spillover sources are indicated in brackets and follow the taxonomy developed in \cite{Stephan_2021}: Other technology (T), other sector (S), other scientific discipline (D).}
    \label{tab:subeff_vfe}
\end{table}
